Data Predictive Control with Random Forests:\\Theory and Applications\tnoteref{mytitlenote}

### 2017-09-29 paper/casestudyReal.tex
small changes

\begin{table}[h!]
	\centering
	\begin{tabular}{ccccc}
		\toprule
		\multirow{3}{1.4cm}{\centering Structural member} & \multirow{3}{3.7cm}{\centering Layer description (from inside to outside)}     & Thermal     		    & Total     & Total        \\
		                                                  &                                                                                & resistance   		    & thickness & U-value      \\
		                                                  &                                                                                & $[(m^2K)/W]$		    & $[m]$     & $[W/(m^2K)]$ \\
		\midrule
		\multirow{3}*{Wall}                               & Wood-cement                                                                    & $0.308$     		    &           &              \\ 
		                            					  & Concrete                                                                       & $0.096$    		    & $0.50 $   & $0.12 $      \\ 
		                            					  & EPS and graphite                                                               & $6.774$    		    &           &              \\
														  &																				   &						&			&			   \\
		\multirow{3}*{Floor}        					  & Screed                                                                         & $0.027$     		    &           &              \\ 
							        					  & Polystyrene                                                                    & $6.000$     		    & $0.23 $   & $0.28 $      \\ 
							        					  & Wood-cement                                                                    & $0.308$     		    &           &              \\
														  &																				   &						&			&			   \\
		\multirow{5}{1.4cm}{\centering Pitched roof} 	  & \multirow{2}{3.7cm}{\centering Polyurethane resins and polyisocianurate foams} & \multirow{2}*{$4.000$} &           &              \\ 
														  &                                                                                &                        &           &              \\
														  & Screed                                                                         & $0.027$    		    & $0.31 $   &  $0.13 $     \\
							        					  & Polystyrene                                                                    & $6.000$    		    &           &              \\ 
							        					  & Wood-cement                                                                    & $0.308 $   		    &           &              \\
		\bottomrule
	\end{tabular}
	\caption{Wood-cement blocks properties.}
	\captionsetup{justification=centering}
	\label{T:houseProperties}
\end{table}

>>>>

\begin{table}[h!]
	\centering
	\begin{tabular}{ccccc}
		\toprule
		\multirow{3}{1.4cm}{\centering Structural member} & \multirow{3}{3.7cm}{\centering Layer 
															description (from inside to outside)}       & Thermal     		     & Total     & Total        \\
		                                                  &                                             & resistance   		     & thickness & U-value      \\
		                                                  &                                             & $[(m^2K)/W]$		     & $[m]$     & $[W/(m^2K)]$ \\

		\midrule
		\multirow{3}*{Wall}                               & Wood-cement                                 & $0.308$     		     &           &              \\ 
		                            					  & Concrete                                    & $0.096$    		     & $0.50 $   & $0.12 $      \\ 
		                            					  & EPS and graphite                            & $6.774$    		     &           &              \\
														  &							                    &						 &		     &			    \\

		\multirow{3}*{Floor}        					  & Wood-cement                                 & $0.308$     		     &           &              \\ 
							        					  & Polystyrene                                 & $6.000$     		     & $0.23 $   & $0.28 $      \\ 
							        					  & Screed                                      & $0.027$     		     &           &              \\
														  &									    	    &					 	 &		     &			    \\

		\multirow{5}{1.4cm}{\centering Pitched roof} 	  & Wood-cement                                 & $0.308$                &           &              \\ 
														  & Polystyrene                                 & $6.000$                &           &              \\
							        					  & Screed                                      & $0.027$                & $0.31 $   & $0.13 $      \\ 
							        					  & \multirow{2}{3.7cm}{\centering Polyurethane 
							        					  	resins and polyisocianurate foams}          & \multirow{2}*{$4.000$} &           &              \\
						        					  	  &                                             &                        &           &              \\
		\bottomrule
	\end{tabular}
	\caption{Wood-cement blocks properties.}
	\captionsetup{justification=centering}
	\label{T:houseProperties}
\end{table}
